\hoofdstuk{appendix II - iStager requirements}

Functional requirements:
\begin{enumerate}
\item \emph{Cross-platform}\\Application must be compatible to run on iOS 4.3 or greater \emph{and} Android 2.2 or greater.
\item \emph{Native look-and-feel}\\Application must make use the of native user interface components.
\item \emph{i18n}\\Application must have language support for both Dutch and English.
\item \emph{Generic style}\\Application must have a configurable stylesheet to generate different styles of user interface looks.
\end{enumerate}
\noindent Feature requirements:
\begin{enumerate}
\item
	List of current and upcoming events
	\begin{enumerate}
		\item events are downloaded in JSON format from the Stager event atomfeed at \texttt{http://<feedurl>/web/feeds/events}
		\item events are displayed in a row-based layout
		\item events are linked to their corresponding event detailview
		\item events in the list are sorted by date (ascending)
		\item events in the list contain labels with event title, subtitle, date
	\end{enumerate}
\item
Detailview of an event, shows detailed event information of an selected event:
\begin{enumerate}
	\item event title, subtitle, date, times (doors open, start, end), location details (venue name, street, number, city), event content (html rendered text)
\end{enumerate}
\item
Add event to agenda
\begin{enumerate}
	\item Prompts the user: "\emph{Add event 'x' on date 'y' in agenda?}"
	\item Adds a selected event to the mobile devices agenda.
	\item Prompts the user of succes of add action.
\end{enumerate}
\item
Start gps-based navigation towards physical location of event
\begin{enumerate}
	\item Prompts the user "\emph{Navigate to y?}" (y in the format of: streetname, housenumber, cityname, postalcode)
	\item Opens map application with address as argument.
\end{enumerate}
\item
View media attached to an event
\begin{enumerate}
	\item Media defined as: URL's to event images, videos, websites.
	\item When selected a media item will be displayed in new window
\end{enumerate}
\item
Display in a grid or list, categorize media types.
\begin{enumerate}
	\item Each displayed media item is resembled by a tumbnail or icon.
	\item When selected a media item opens to its content in:
	\item images an included webview,
	\item websites the device browser,
	\item for videos the youtube app or the browser( depending on video type \& location).
\end{enumerate}
\item
Share event details to social media
\begin{enumerate}
	\item An event detail view will contain a 'share/deel' button.
	\item Prompts the user for platform to share. (twitter/facebook/email)
	\item Default value (editable): "\emph{I am attending event x on date y in location x !}"
\end{enumerate}
\item
(Un)Register device to receive push notifications on new events of interest
\item
Register the device to receive pushed notifications about upcoming events which might be of interest to the user.
Based on Relation.interest model in Stager.
\end{enumerate}
